Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-13 ms.tex
I showed what the MORIS photometry time series looks like and how it affects the spectrum.

\clearpage
\pagebreak
\subsection{Mie scattering}

@@

>>>>

\clearpage
\pagebreak
\subsection{Mie scattering MCMC}

@@

\clearpage
\pagebreak
\subsection{MORIS Data}

I made a time series of my photometry to see if it would help with the spectrum fit.

The SNR is so low that's it hard to see any clear pattern.
The photometry adds very little to the spectrum, as seen in Figure \ref{fig:morisPhotometryAndSpec}.

\begin{figure*}[!t]
\centering
\subfloat[MORIS $i$ Band Photometry for \shb]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_moris_tser_best_fit.pdf}
	\label{fig:morisTSerBestFit}
	}
\subfloat[Amplitude spectrum for \shb\ when adding MORIS photometry]{
	\includegraphics[width=0.5\textwidth]{2mass_1821_a1_spec_w_moris.pdf}
	\label{fig:spectrum1821WMoris}
	}
	\caption{MORIS photometry does not significantly improve the constraints on the spectrum.}
	\label{fig:morisPhotometryAndSpec}
\end{figure*}
